Declarative Probabilistic Logic Programming\\in Discrete-Continuous Domains

### 2024-09-10 202409_aij_dc_problog_aij_second/files_old/types.tex
aij dcproblog paper

\section{\dcproblogsty Syntax and Type System} \label{sec:syntax}
\ak{I propose to move the type system and multiple dispatch stuff to a separate implementation section as much as possible;\ie, from here onwards: 1) introduce DC-ProbLog programs as normal logic program + probabilistic facts + distributional facts + comparison predicates instead of wrapped query terms, 2) show that these map to DC-PLP, 3) add further syntactic sugar (is/2, distributional clauses, anything else? are annotated disjunctions part of DC-ProbLog?) and show how that maps back onto the basic version, 4) talk about multiple dispatch and all that }

\todo{this is just moved from earlier sec 3, needs linking to DC-PLP and merging with semantics in next section; the goal is to introduce DC-ProbLog as a higher level modeling language that makes concrete choices for the reserved functors in DC and introduces nicer syntax / syntactic sugar, but for its semantics maps back to (an instance of) DC-PLP}

\subsection{Type System}
Before we formally specify the syntax of \dcproblogsty, we specify a hierarchical type system. To this end we will modify the type system given in~\citep{sterling1994art}, one of the main references on \prologsty. The base type in the type system of~\citep{sterling1994art} is the \type{Term} type, from which other types are subtyped. In other words: everything is a \type{Term}.
\begin{enumerate}
	\item[]   \type{Term}
	\begin{itemize}		
		\item \type{Atomic}
		\begin{itemize}
			\item \type{Atom}
			\item \type{Number}
		\end{itemize}
		\item \type{Compound}
	\end{itemize}
\end{enumerate}

{\em Logical variables} (technically referred to as {\em meta-logical variables}~\citep[Chapter 10]{sterling1994art}) are omitted from the type system hierarchy, as they can ground to any type, depending on the context. In Figure~\ref{fig:type_system_prolog} we give a diagrammatic representation of the \prologsty type system.
Note that \problogsty uses a different nomenclature: atom terms in \problogsty correspond to the union of atom terms and compound terms in the \prologsty nomenclature of~\citep{sterling1994art}. In a first step we are going to change the \prologsty type system to match the nomenclature of \problogsty.
\begin{enumerate}
	\item[]   \type{Term}
	\begin{itemize}		
		\item \type{Number}
	\end{itemize}
	\begin{itemize}
		\item \type{Atom}
	\end{itemize}
\end{enumerate}

In Table~\ref{table:comp_type_system} we give a side by side comparison of the two type systems and in Figure~\ref{fig:type_system_prolog} and~\ref{fig:type_system_problog} we give diagrammatic representations of both type systems.

\begin{table}[h]
	\caption{Comparison of the \prologsty type system and the \problogsty type system.}
	\label{table:comp_type_system}
	\begin{center}
		\begin{tabular}{c||c|c|c}
			example \type{Term} & \multicolumn{2}{c|}{\prologsty} & \problogsty \\ 
			\hline
			\probloginline{3} & \type{Number} & \multirow{2}{*}{\type{Atomic}}  &  \type{Number}  \\
			\cline{1-1} \cline{4-4}
			\probloginline{foo} & \type{Atom} &   & \multirow{2}{*}{\type{Atom}}  \\
			\cline{1-3}
			\probloginline{bar(foo)} &  \multicolumn{2}{c|}{\type{Compound}}  &   \\
			%	\probloginline{foo} & \begin{tabular}{@{}c|c@{}}
			%		\type{Atom} &\multirow{0}{c}{\phantom{\type{Atomic}}} 
			%	\end{tabular}  &  \type{Atom} \\
		\end{tabular}
	\end{center}
\end{table}

\begin{figure}[h!]
	\centering
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=0.85\linewidth]{../figures/type_hierarchy_prolog.pdf}
	\end{minipage}%
	\hfill
	\begin{minipage}{.45\textwidth}
		\centering
		\includegraphics[width=0.85\linewidth]{../figures/type_hierarchy_problog.pdf}
	\end{minipage}
	\par
	\medskip
	\noindent
	\begin{minipage}[t]{.45\textwidth}
		\captionof{figure}[Diagrammatic representation of the hierarchical \prologsty type system.]{Diagrammatic representation of the hierarchical \prologsty type system~\citep{sterling1994art}. The \type{Number} type is further subtyped into \type{Integer} and \type{Float}.}
		\label{fig:type_system_prolog}
	\end{minipage}%
	\hfill
	\begin{minipage}[t]{.45\textwidth}
		\captionof{figure}[Diagrammatic representation of the hierarchical \problogsty type system.]{Diagrammatic representation of the hierarchical \problogsty type system. The \type{Number} type is further subtyped into \type{Integer} and \type{Float}.}
		\label{fig:type_system_problog}
	\end{minipage}
\end{figure}

Analogously to the just introduced type system of \problogsty, the base type for \dcproblogsty is again the \type{Term} type. At this point we modify the \problogsty type system by subtyping terms with a \type{Distrbution} type and a \type{Symbol} type. 
Dividing \dcproblogsty terms into \type{Distribution} terms and \type{Symbol} terms reflects the characterization of~\citet{poole2010probabilistic} of probabilistic programs as being constituted of independent choices (\type{Distribution}) and a deterministic system (\type{Symbol}).

\begin{definition}\label{def:type_system}
	The \dcproblogsty type system is a hierarchical type system with each type being a disjoint union of its subtypes.
	\begin{enumerate}
		\item[] \type{Term} 
		\begin{enumerate}
			\item[1.] \type{Distribution}
			\begin{itemize}
				\item \type{DiscreteD}
				\item \type{ContinuousD}
				\item \type{MixtureD}
			\end{itemize}
			\item[2.] \type{Symbol}
			\begin{itemize}		
				\item \type{Arithmetic}
				\begin{itemize}
					\item  \type{RandomVariable}
					%			\begin{itemize}
					%				\item \type{DiscreteRV}
					%				\item \type{ContinuousRV}
					%				\item \type{MixtureRV}
					%			\end{itemize}
					\item \type{Number}
				\end{itemize}
				\item \type{Atom}
			\end{itemize}
		\end{enumerate}
	\end{enumerate}
\end{definition}

A diagrammatic overview of the \dcproblogsty type system is given in Figure~\ref{fig:type_system}.

\begin{figure}[t]
	\begin{center}
		\includegraphics[width=\linewidth]{../figures/type_hierarchy.pdf}
	\end{center}
	\caption[Diagrammatic representation of the hierarchical \dcproblogsty type system.]{Diagrammatic representation of the hierarchical \dcproblogsty type system. Compared to Definition~\ref{def:type_system},  the \type{Number} type is further subtyped into \type{Integer} and \type{Float} types and the \type{RandomVariable} type is subtyped into \type{DiscreteRV}, \type{ContinuousRV}, and \type{MixtureRV}. These subtypes of \type{RandomVariable} mimic the subtypes of the \type{Distribution} type.}
	\label{fig:type_system}
\end{figure}

%A type is a disjoint union of its subtytpes, for example:
%$$\type{Term}=\type{Distribution} \cup \type{Symbol}$$

\subsubsection{Distribution Terms}
As already seen in Examples~\ref{example:dcproblog_machine} and~\ref{example:dcproblog_poisson_population}, \type{Distribution} terms determine the probability distribution according to which a random variable is distributed.

\begin{definition}[\type{Distribution}]
	Terms of type \type{Distribution} are constructed by using a reserved random function symbol and applying it to a (possible empty) tuple of input arguments, which maps the input tuple to a distribution term.
	Distribution terms are only allowed to be invoked as a second argument to the reserved distribution predicate \probloginline{is}\lstinline[columns=fixed]|/2|.
	This also means that random function symbols are only used there as well. \dcproblogsty subtypes the \type{Distribution} type into the \type{DiscreteD}, \type{ContinuousD}, and \type{MixtureD} types.
\end{definition}

\probloginline{poisson(6)} and \probloginline{normal(20,5)} are for instance of types \type{DiscreteD} and  \type{ContinuousD}, respectively.
Note that distributions of type \type{ContinuousD} denote {\em absolutely continuous} probability distributions\footnote{\dcproblogsty does not support {\em singular continuous} probability distributions such as the Cantor distribution.}. \ak{would be nice to have a hint on why this restriction is there} We give an example of a distribution of type \type{MixtureD} in Example~\ref{ex:indian_gpa_function}.
%\begin{example} \probloginline{mixed} is a random variables that is a mixture of a continuous part (the truncated normal between $0$ and $4$ with mean $3$ and standard deviation $1$) and a discrete part. 
%\begin{problog}
%mixted~Mix((0.998,TruncNormal(3,1,0,4)),(0.001,4),(0.001,4))
%\end{problog}
%\end{example}

%For and example, see Example~\ref{example:dcproblog_poisson_population}: we have the random function symbol \probloginline{poisson}\lstinline[columns=fixed]{/1}, apply it to the input tuple \probloginline{(6)}, and obtain a term of type \type{Distribution}.

\subsubsection{Symbol Terms}
\type{Symbol} terms are the building blocks of the discrete structure that makes up a logic program and as such determine also the deterministic system of a probabilistic logic program. Beyond the reserved syntax, which is used to define the distribution terms, the user is free to use any identifier (following \prologsty conventions) to declare \type{Symbol} terms -- this includes standard \prologsty terms such as lists.
%The subtyping of the \type{Symbol} type (shown in Figure~\ref{fig:type_system}) follows the convention given in~\citep[Chapter 9]{sterling1994art}.

\begin{definition}[\type{Arithmetic}]
	Terms of type \type{Symbol} for which arithmetic operations are defined are of type \type{Arithmetic}. \type{Arithmetic} terms can be used as second argument to the builtin \probloginline{is}\lstinline[columns=fixed]|/2| functor. \type{Arithmetic} terms are subtyped with \type{RandomVariable} terms and \type{Number} terms.
%	\ak{Def 6.3 Arithmetic terms: if (as stated in def 6.1) each type is the disjoint union of its subtypes, that means that "arithmetic" is made up exclusively of numbers and RVs, \ie, terms like 3-2 or min(x,5) for a RV x are not allowed, whereas the first two sentences of def 6.3 suggests they might be allowed (only having numbers and RVs directly on the rhs of is/2 seems quite boring...). Which is it?
%		Related to this, defs 6.8 and 6.10 talk about RVs and Numbers, why not simply "arithmetic"?}
\end{definition}
We talk in more detail about \type{Arithmetic} terms and their evaluation in Subsection~\ref{sec:arithmetic}.

\begin{definition}[\type{RandomVariable}] \label{def:random_variable}
	\type{RandomVariable} terms are named by the programmer using distributional facts with the binary infix predicate \probloginline{is}\lstinline[columns=fixed]|/2| and inherit their subtype from the distribution term. All random variables present in a \dcproblogsty program are named. \type{RandomVariable} terms are a subtype of the \type{Arithmetic} type. \ak{Def 6.4: why do you restrict random variables to be arithmetic? What about color(Ball)~uniform([red,green,blue])? Of course, such finite discrete domains could be encoded using integers and then translated back in the LP, so theoretically speaking it's probably not a restriction to only have numbers, but from a modeling perspective, it is surprising to me.}
\end{definition}

Examples of terms of type \type{RandomVariable} would be \probloginline{temperature} and \probloginline{n_people} in Examples~\ref{example:dcproblog_machine} and~\ref{example:dcproblog_poisson_population}, where we declared the random variables through so-called {\em distributional facts}: 
\begin{problog}
temperature ~ normal(20,5).
n_people ~ poisson(6).
\end{problog}
As mentioned in Defintion~\ref{def:random_variable}, \type{RandomVariable} terms inherit their type from the associated \type{Distribution} term, \eg a \type{ContinuousD} term induces a random variable term of type \type{ContinuousRV}.

Note that not all probabilistic programming languages enforce the naming of random variables. In the functional probabilistic programming language \anglicansty~\citep{wood2014approach}, for instance, the user can declare anonymous random variables, much like anonymous functions, \ie \textlambda-functions.
\ak{Discussion of named/unnamed between Defs 6.4 and 6.5: would be nice to have a brief hint on why you made that choice}

\begin{definition}[\type{Number}] Terms of type \type{Number} are used to express numerical data types such as integers and floating point numbers.	
\end{definition}

\ak{terminology mix-up; predicates never form terms}
\begin{definition}[\type{Atom}]
	An atom is of the form \probloginline{p(t@$_1$@,@\dots @, t@$_n$@ )} where \probloginline{p} is a predicate of arity $n$ and the \probloginline{t@$_i$@} are \type{Symbol} terms~\citep{fierens2015inference}. Predicates used to construct \type{Atom} terms must not clash with the builtin predicates and reserved random function symbols used to declare \type{Distribution} terms. Terms of type \type{Atoms} constitute the building blocks of the discrete structure of a probabilistic logic program.
\end{definition}

Examples of atoms terms would be \probloginline{foo} or \probloginline{bar(foo,42)}. The latter is constructed using the predicate \lstinline{bar/2} and the tuple of \type{Symbol} terms \probloginline{(foo,42)}. \probloginline{foo} is of type \type{Atom} and \probloginline{42} is a \type{Number} term.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Syntax}
%Based on the type system, we now define the syntactic components of DC-ProbLog and its syntax.
\begin{definition}[Deterministic Rules and Facts]
	A (normal) logic program is a set of rules. A rule is a universally quantified expression of the form
	\begin{problog}
h:- b@$_1$@, @\dots@, b@$_n$@.
	\end{problog}
	where \probloginline{h} is an \type{Atom} term and $\{ \text{\probloginline{b@$_1$@}}, \text{\dots},\text{\probloginline{b@$_n$@}} \}$ is a set of $n$ literals.
	Literals are either \type{Atom} terms, or their negation.
	The \type{Atom} term \probloginline{h} is called the head of the rule and \probloginline{b@$_1$@, @\dots@, b@$_n$@} the body. The latter represents the
	conjunction $\text{\probloginline{b@$_1$@}} \land \cdots \land  \text{\probloginline{b@$_n$@}}$. A fact is a rule that has \probloginline{true} as its body and is simply written as
	\begin{problog}
h.
	\end{problog}
\end{definition}

\begin{definition}[Probabilistic Facts]
	Probabilistic facts are of the form \probloginline{p::fact}. \probloginline{p} is a term of type \type{Number} or \type{RandomVariable}, with $0{\leq} \text{\probloginline{p}} {\leq} 1$  and \probloginline{fact} is a ground atom. 
	%\begin{definition} A {\bf probabilistic fact} is a ground definite fact labeled with a probability.
\end{definition}

\begin{definition}[Distributional Facts]
	Distributional facts introduce random variable terms and associate them with a distribution using the reserved binary predicate \probloginline{~}\lstinline[columns=fixed]|/2| in infix notation. A distributional fact is a ground fact of the form \probloginline{rand ~ distribution}, where \probloginline{distribution} is a well-typed distribution term with output type \type{DistributionX} and \probloginline{rand} is a ground term whose functor is not reserved. The distributional fact introduces \probloginline{rand} as a random variable of type \type{RandomVariableX}, \ie the type of the random variable term mimics the type of the distribution term.
\end{definition}
Distributional facts can be thought of as the link between the independent choices (in form of distributions) and the discrete structure (in form of rules and facts).

\begin{definition}[Comparison predicates] \label{def:comparison}
	\dcproblogsty (similar to \prologsty and \problogsty) uses a fixed set of builtin binary predicates whose truth values depend on the \emph{evaluation} of its arguments. For terms that can be evaluated (\type{RandomVariable} terms and \type{Number} terms) we use the set
	$\bowtie=\{ \text{\probloginline{=:=}}, \text{\probloginline{=\=}}, \text{\probloginline{<}}, \text{\probloginline{>}},  \text{\probloginline{=<}}, \text{\probloginline{>=}} \}$
	of binary predicates written in infix notation.
	Each of these has the usual \prologsty arithmetic interpretation of evaluating each side and comparing the results.
	Just as for \prologsty arithmetic, truth values of atoms using these predicates are determined through an evaluation process that is external to the (probabilistic) logic program. Such atoms can be used in clause bodies, but never in clause heads (or as facts).
\end{definition}

%We will further discuss arithmetic evaluations in Subsection~\ref{sec:arithmetic}.

\begin{example} Comparison predicates allow for the comparison of random variables to numbers. 
	\begin{problog*}{linenos}
x ~ normal(0,3).
q:- x>0.
query(q).
	\end{problog*}
\end{example}

%\begin{definition}\label{def:distributional_fact}
%	A {\bf distributional fact} is a ground definite fact with the reserved binary predicate \probloginline{is}\lstinline[columns=fixed]|/2| used in infix notation.
%\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Multiple Dispatch} \label{ref:multiple_dispatch}
The attentive reader might have noticed that in Definition~\ref{def:comparison} we used the same comparison predicates, for \type{RandomVariable} terms as well as \type{Number} terms. In \dcproblogsty we resolve this clash through {\em multiple dispatching}\citep{castagna1995calculus}.
{ Multiple dispatching} is the process of dynamically selecting at run time\footnote{In the context of logic programming we understand as run time the time it takes to ground the logic program part of a \dcproblogsty program.} a specific implementation of a function based on the types of the arguments that are fed as input to the corresponding function symbol.
Such functions are referred to as {\em multimethods}. 
An early example of multiple dispatch is the {\em Common Lisp Object System}~\citep{keene1989object}. Multiple dispatch is also the programming paradigm on which the \juliasty programming language is built~\citep{bezanson2017julia}. We reuse this idea in the context of probabilistic logic programming with random function symbols to retain a simple and neat syntax.
Consider, for instance, the declaration of the normal distribution in Example~\ref{example:dcproblog_machine}.
The definition of the function is the following:
$$ \text{\probloginline{normal}}: \type{Number} \times \type{Number} \rightarrow \type{ContinuousD}$$
However, the arguments of a normal distribution (its mean and standard deviation) might as well be random variables themselves.
Multiple dispatching then allows us to {\em overload} the \probloginline{normal} function symbol by using arguments of a different type\footnote{For simplicity we omit that the standard deviation has to be a strictly positive (real) number, which can be enforced by extending the type system.}:
\begin{align*}
	\text{\probloginline{normal}}&: \type{RandomVariable} \times \type{Number} \rightarrow \type{ContinuousD} \\
	\text{\probloginline{normal}}&: \type{Number} \times \type{RandomVariable} \rightarrow \type{ContinuousD} \\
	\text{\probloginline{normal}}&: \type{RandomVariable} \times \type{RandomVariable} \rightarrow \type{ContinuousD}
\end{align*}
The exact implementation of these random function symbols is left to the designer of the implementation of the language.
%In the next Subsection~\ref{sec:arithmetic} we will encounter further usages of multiple dispatching in \dcproblogsty.

@@

\begin{example} A \dcproblogsty code snippet showing how random variable terms can be used in an arithmetic expression. 
	\begin{problog*}{linenos}
x ~ normal(0,3).
q:- X is x+3, X>3.
query(q).
	\end{problog*}
\end{example}

@@

\subsubsection*{Strongly Typed \prologsty}

>>>>

\section{System Predicates and Arithmetic Evaluations}

Every Prolog implementation reserves some predicate names for
system-related procedures. Queries to these predicates, called system
predicates, are handled by special code in the implementation in contrast
to calls to predicates denned by pure Prolog programs.

builtin predicates

The role of the system predicates for arithmetic introduced in Prolog is
to provide an interface to the underlying arithmetic capabilities of the
computer in a straightforward way. The price paid for this efficiency is
that some of the machine-oriented arithmetic operations are not as gen-
general as their logical counterparts. The interface provided is an arithmetic
evaluator, which uses the underlying arithmetic facilities of the com-
computer.

\subsubsection{Arithmetic Evaluation}
\todo{write a paragraph introducing the use of is/2 and define its semantics}

\ak{for the cases where the lhs of is/2 ends up in a comparison atom (such as Example \ref{ex:is}), it should be enough to replace is/2 by unification and thereby delay evaluation until the comparison is externally evaluated, but if we also have "regular" uses of is/2, where the (deterministic?) result is \eg returned as an answer, then things get a bit more complex; as I don't know what uses are intended (and valid), this is for someone else to draft... (or it might be that this is really an engine rather than a language thing, in which case it should only be discussed later with the general multiple dispatch stuff)}

\ak{this sec is for Pedro to fix / integrate -- I think a lot of the Prolog type system discussion is not needed for the purpose of this paper; note that the old tex file is still there if needed again}

\dcproblogsty's type system refines the one of DC-PLP to instantiate a conrete version of the abstract language.  Specifically, we have the following refinements:
\begin{enumerate}
    \item distribution functors are further partitioned into \emph{discrete distribution functors}. \emph{continuous distribution functors} and \emph{mixture distribution functors}
    \item arithmetic functors are further partitioned into \emph{operation functors} and \emph{number functors}, with the latter in turn partitioned into \emph{integers} and \emph{floats} \todo{do we have / want a complete list of operations? should we at least give some examples?}
    \item we use Boolean query functors 	$\bowtie=\{ \text{\probloginline{=:=}}, \text{\probloginline{=\=}}, \text{\probloginline{<}}, \text{\probloginline{>}},  \text{\probloginline{=<}}, \text{\probloginline{>=}} \}$
	in infix notation (and lift them to predicate level as discussed before)
\end{enumerate}

\ak{I don't think we need to sub-type random variable functors here, as rv terms inherit the \emph{output} type of the distribution only, which should be integer, float etc, not "discrete distribution"}

\probloginline{poisson(6)} and \probloginline{normal(20,5)} are for instance of types \type{DiscreteD} and  \type{ContinuousD}, respectively.
Note that distributions of type \type{ContinuousD} denote {\em absolutely continuous} probability distributions\footnote{\dcproblogsty does not support {\em singular continuous} probability distributions such as the Cantor distribution.}. \ak{would be nice to have a hint on why this restriction is there} We give an example of a distribution of type \type{MixtureD} in Example~\ref{ex:indian_gpa_function}.

\subsection{Multiple Dispatch} \label{ref:multiple_dispatch}
The attentive reader might have noticed that in Definition~\ref{def:comparison} we used the same comparison predicates, for \type{RandomVariable} terms as well as \type{Number} terms. In \dcproblogsty we resolve this clash through {\em multiple dispatching}\citep{castagna1995calculus}.
{ Multiple dispatching} is the process of dynamically selecting at run time\footnote{In the context of logic programming we understand as run time the time it takes to ground the logic program part of a \dcproblogsty program.} a specific implementation of a function based on the types of the arguments that are fed as input to the corresponding function symbol.
Such functions are referred to as {\em multimethods}. 
An early example of multiple dispatch is the {\em Common Lisp Object System}~\citep{keene1989object}. Multiple dispatch is also the programming paradigm on which the \juliasty programming language is built~\citep{bezanson2017julia}. We reuse this idea in the context of probabilistic logic programming with random function symbols to retain a simple and neat syntax.
Consider, for instance, the declaration of the normal distribution in Example~\ref{example:dcproblog_machine}.
The definition of the function is the following:
$$ \text{\probloginline{normal}}: \type{Number} \times \type{Number} \rightarrow \type{ContinuousD}$$
However, the arguments of a normal distribution (its mean and standard deviation) might as well be random variables themselves.
Multiple dispatching then allows us to {\em overload} the \probloginline{normal} function symbol by using arguments of a different type\footnote{For simplicity we omit that the standard deviation has to be a strictly positive (real) number, which can be enforced by extending the type system.}:
\begin{align*}
	\text{\probloginline{normal}}&: \type{RandomVariable} \times \type{Number} \rightarrow \type{ContinuousD} \\
	\text{\probloginline{normal}}&: \type{Number} \times \type{RandomVariable} \rightarrow \type{ContinuousD} \\
	\text{\probloginline{normal}}&: \type{RandomVariable} \times \type{RandomVariable} \rightarrow \type{ContinuousD}
\end{align*}
The exact implementation of these random function symbols is left to the designer of the implementation of the language.
%In the next Subsection~\ref{sec:arithmetic} we will encounter further usages of multiple dispatching in \dcproblogsty.

@@

\begin{example}\label{ex:is} A \dcproblogsty code snippet showing how random variable terms can be used in an arithmetic expression. 
	\begin{problog*}{linenos}
x ~ normal(0,3).
q:- X is x+3, X>3.
query(q).
	\end{problog*}
\end{example}

@@

\subsubsection*{Strongly Typed \prologsty}
\ak{move to related work?}
